---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```

# R code for *Antimicrobial exposure is associated with decreased survival in triple-negative breast cancer*

<!-- badges: start -->

<!-- badges: end -->

<Paper reference/link to be added here>

## Overview

We used Oncoshare, a breast cancer research database that integrates electronic medical records with California Cancer Registry data for patients treated for breast cancer at Stanford University Healthcare and/or several sites of the community-based Sutter Health network, to study the association of antimicrobial exposure during cancer treatment and follow-up and survival in the presence of time-varying absolute lymphocyte count. In this repository, which we call TNBC_MSM, we provide methods to associate an exposure with a survival outcome in the presence of a related time-varying covariate. We also provide methods for several sensitivity analyses and deidentified datasets for analyses.

## Repository Contents

-   R source code (TNBC_MSM/R)

    -   poisson_ipwtm.R - *Source code for the function responsible for fitting the Poisson MSM. Adapted from ipw::ipwtm()*
    -   TNBC_analyses.R - *R code for all analyses performed. Output objects are saved in "TNBC_MSM/output"*

-   Deidentified datasets ('TNBC_MSM/data')

    -   clean_meds.xlsx - *medications data presented in Supplemental Table 1*
    -   TNBC_data_baseline.rds - *deidentified baseline cross-sectional data with embedded labels. Available upon request.*
    -   TNBC_data_longitudinal.rds - *deidentified baseline longitudinal data with embedded labels. Available upon request.*

-   TNBC_Results.Rmd - *Rmarkdown file responsible for rendering all tables and figures. Outputs "TNBC_Results.html" as final report document.*

## System Requirements

**Hardware Requirements:** the TNBC_MSM repository requires a standard computer with a minimum of 2 GB of RAM. The runtimes below are generated using a M1 Macbook Pro, 16 Gb RAM, macOS Version 13.2.1.

**Software Requirements:** before setting up the TNBC_MSM repository, users should have R version 4.1.0 or higher (available at (<https://cran.rstudio.com/>)

The installation of R should take about 20 seconds.

## Installation Guide

**Package dependencies:** users should install the following packages prior to installing TNBC_MSM, from an R terminal: `dplyr`, `ggplot2`, `ipw`, `survival`, `survminer`, `finalfit`, `table1`, `geepack`, `forcats`, `forestplot`, `gtsummary`, `patchwork`.

**Demo and Results:** to run the analyses and render the final html report, the user should compile the `.Rmd` files by submitting the line below on the R console.

```{r, eval=FALSE}
rmarkdown::render('TNBC_Results.Rmd')
```
